Deep Reinforcement Learning for Conservation Decisions

### 2021-05-06 manuscript/manuscript.Rmd
minor comments
draft conceptual figure

@@

@@

Should we mention SARSA, Double DQN?  
Can we add HER (since delayed reward case may be particularly interesting)
Should we do anything to better reflect the 'family tree' here? (e.g. DQN -> DDPG -> TD3)

>>>>

\begin{figure}
\centering
\includegraphics[width=0.8\linewidth]{fig1.pdf}
\caption{Reinforcement Learning focuses on the repeated feedback of *agent* interacting with an *environment*. The agent performs an action which influences the environment's future *state*.  The agent recieves an observation of the new state and reward from the environment.}
\end{figure}

@@

I think we can lean more heavily both in references to and paralleling the presentation of some of the existing background material.

@@

Should we mention:

- Temporal Differencing, RIENFORCE
- SARSA, 
- Double DQN?  
Can we add HER (since delayed reward case may be particularly interesting)
Should we do anything to better reflect the 'family tree' here? (e.g. DQN -> DDPG -> TD3)
